---
title: "p8105_hw1_qc2307"
author: "Qixiang Chen"
date: "9/28/2021"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Question 1

This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

Create a data frame comprised of:

a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”
Try to take the mean of each variable in your dataframe. What works and what doesn’t?

Hint: to take the mean of a variable in a dataframe, you need to pull the variable out of the dataframe. Try loading the tidyverse and using the pull function.

In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

```{r}
library(tidyverse)
set.seed(123)
problem1_df = tibble(
  ## a random sample of size 10 from a standard Normal distribution
  randomNums = rnorm(10),
  ## a logical vector indicating whether elements of the sample are greater than 0
  logical_ifPositive = (randomNums > 0),
  ## a character vector of length 10
  introduction = c("Hello", "Everyone", "My", "Name", "Is", "Qixiang", "Chen", "Call", "Me", "Shawn"),
  ## a factor vector of length 10, with 3 different factor "levels" which are size S, size M, and size L.
  size = factor(c("S", "M", "L", "L", "L", "L", "S", "M", "S", "L")),
)
problem1_df
mean(pull(problem1_df, randomNums))
mean(pull(problem1_df, logical_ifPositive))
mean(pull(problem1_df, introduction))
mean(pull(problem1_df, size))
```
In this case, only numeric vector and logical vector can generate a mean, while the character vector and the factor cannot generate a mean by using "mean()".

```{r}
mean(pull(problem1_df, as.numeric(introduction)))
mean(pull(problem1_df, as.numeric(size)))
```

In the case, I tried to use "as.numeric" function to transform the character vector and the factor vector to numeric datatype, it does not work at all. It implies that "as.numeric" function will not work inside the "mean()" function.


# Question 2

### Short Description
This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.
Next, use the following code (in your RMarkdown file) to load the penguins dataset:
data("penguins", package = "palmerpenguins")
Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:
the data in this dataset, including names / values of important variables
the size of the dataset (using nrow and ncol)
the mean flipper length

```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
row = nrow(penguins)
column = ncol(penguins)
mean_flipper_length = mean(na.omit(pull(penguins, flipper_length_mm)))
```
In the "penguins" dataset, there are several important variables including species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, and body_mass_g. In this dataset, there are `r row` rows and `r column` columns. The mean of flipper length is `r mean_flipper_length`.

### Sketch a scatterplot
Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).
Export your first scatterplot to your project directory using ggsave.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```


